---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source: embed
---

```{r setup, include=FALSE}
library(tidyverse)
library(flexdashboard)
library(plotly)
library(p8105.datasets)
data("ny_noaa")
```
## Column {data-width="650"}

We will work on observations with id "USC00300023", "USC00301152", and "USC00304912" in 2001 without NAs.
```{r}
weather_df = 
  ny_noaa %>% 
  na.omit() |> 
  separate(date, into = c("year", "month", "day"), convert = TRUE) %>% 
  mutate(
    month = factor(month, levels = 1:12),
    tmax = as.numeric(tmax),
    tmin = as.numeric(tmin)) |> 
  filter(
    year == 2001,
    id %in% c("USC00300023", "USC00301152", "USC00304912"))
```

### Scatterplots

In this scatterplot, we will look into the relation between tmax and tmin across months.
```{r}
scatterplot = 
  weather_df |> 
  plot_ly(x = ~tmin,
    y = ~tmax,
    color = ~month,
    type = "scatter",
    mode = "markers",
    colors = "viridis",
    text = ~month, alpha = 0.3) |> 
  layout(
    title = "tmax vs tmin across months",
    xaxis = list(title = "tmin"),
    yaxis = list(title = "tmax")
  )

scatterplot

```

## Column {data-width="350"}

### boxplot
In this boxplot, we will look into the distribution of tmax across months.
```{r}
boxplot = 
  weather_df |> 
  plot_ly(x = ~month, y = ~tmax, type = "box", color = ~month,colors = "viridis") %>%
  layout(
    title = "distribution of tmax across months",
    xaxis = list(title = "month"),
    yaxis = list(title = "tmax")
  )

boxplot
```

### barplot
In this boxplot, we will compare the total precipitation across months.
```{r}
barplot = 
  weather_df |> 
  group_by(month) |> 
  summarize(sum_prcp = sum(prcp)) |> 
  plot_ly(x = ~month, y = ~sum_prcp, color = ~month, type = "bar", colors = "viridis") |> 
  layout(
    title = "total precipitation across months",
    xaxis = list(title = "month"),
    yaxis = list(title = "total precipitation")
  )

barplot

```
